Manuscript results

### 2024-03-28 05_report/Manuscript_results_temp.Rmd
pushed

```{r}
fileloc <- here::here("04_analysis","output","scenarios","sickkids control lnorm lifetime combo")
index <- c(1:50)
```

@@

df_AE0 <- rbind(df_AE_Targeted, df_AE_SoC)
df_AE <- as.data.frame(apply(df_AE0, 2, cumsum))
df_AE$cycle <- df_AE0$cycle
df_AE$intervention <- df_AE0$intervention

prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Cumulative Incidence of PLGG-related AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG-related AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> a

prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
                                intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Cumulative Incidence of Other AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "Other AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> b
grid.arrange(a,b, nrow=2, ncol=1)
```

>>>>

```{r}
fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime investigator combo")
index <- c(1:30)
nn <- length(index)
```

@@

df_AE_Targeted0 <- as.data.frame(apply(df_AE_Targeted, 2, cumsum))
df_AE_Targeted0$cycle <- df_AE_Targeted$cycle
df_AE_Targeted0$intervention <- df_AE_Targeted$intervention
df_AE_SoC0 <- as.data.frame(apply(df_AE_SoC, 2, cumsum))
df_AE_SoC0$cycle <- df_AE_SoC$cycle
df_AE_SoC0$intervention <- df_AE_SoC$intervention
df_AE <- rbind(df_AE_Targeted0, df_AE_SoC0)

prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Cumulative Incidence of PLGG-related AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG-related AE states") +
  theme_bw() +
  scale_y_continuous(limits=c(0,0.5)) + 
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> a

prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
                                intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Cumulative Incidence of Other AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "Other AE states") +
  theme_bw() +
  scale_y_continuous(limits=c(0,0.5)) + 
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> b
grid.arrange(a,b, nrow=2, ncol=1)
```
